Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-07-26 ms.tex
Make acronyms more uniform

A \ac{CBC} source is specified by a vector of extrinsic parameters describing its position and orientation and intrinsic parameters describing the physical properties of the binary components:
%
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                D_\mathrm{L} \\
                t_\oplus \\
                u \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    luminosity distance \\
                    arrival time at geocenter \\
                    $\cos(\textrm{inclination angle})$ \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic parameters}, \boldsymbol\theta_\mathrm{ex} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic parameters}, \boldsymbol\theta_\mathrm{in}
            \end{array}
        \end{array}
\end{equation}
%
Even this list of parameters involves some simplifying assumptions. First, for \ac{BNS} systems, we omit binary eccentricity as an intrinsic parameter because tidal interaction of the progenitor stars~\cite{0004-637X-572-1-407} and later \ac{GW} emission~\cite{PhysRev.136.B1224} circularize the orbit long before the inspiral enters \ac{LIGO}'s frequency range of $\sim$10\nobreakdashes--1000~kHz. Eccentricity would play a major role in the evolution and waveforms of \ac{NSBH} and \ac{BBH} sources formed by dynamical capture~\cite{PhysRevD.87.043004}. Tidal deformabilities of the \acp{NS} are omitted because the effect of tides on the inspiral would only be detectable by an Einstein Telescope-class \ac{GW} observatory~\cite{PhysRevD.81.123016}. Furthermore, in \ac{GW} detection efforts, especially those focused on \ac{NSNS} systems, the component spins $\mathbf{S}_1$ and $\mathbf{S}_2$ are often assumed to be nonprecessing and aligned with the system's total angular momentum and condensed to a single scalar parameter $\chi$, or even neglected entirely, $\mathbf{S}_1 = \mathbf{S}_2 = 0$. In this work we will not consider spin precession.

>>>>

A \ac{CBC} source is specified by a vector of extrinsic parameters describing its position and orientation and intrinsic parameters describing the physical properties of the binary components:
%
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                D_\mathrm{L} \\
                t_\oplus \\
                u \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    luminosity distance \\
                    arrival time at geocenter \\
                    $\cos(\textrm{inclination angle})$ \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic parameters}, \boldsymbol\theta_\mathrm{ex} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic parameters}, \boldsymbol\theta_\mathrm{in}
            \end{array}
        \end{array}
\end{equation}
%
Even this list of parameters involves some simplifying assumptions. First, for \ac{BNS} systems, we omit binary eccentricity as an intrinsic parameter because tidal interaction of the progenitor stars~\cite{0004-637X-572-1-407} and later \ac{GW} emission~\cite{PhysRev.136.B1224} circularize the orbit long before the inspiral enters \ac{LIGO}'s frequency range of $\sim$10\nobreakdashes--1000~kHz. Eccentricity would play a major role in the evolution and waveforms of \ac{NSBH} and \ac{BBH} sources formed by dynamical capture~\cite{PhysRevD.87.043004}. Tidal deformabilities of the \acp{NS} are omitted because the effect of tides on the inspiral would only be detectable by an Einstein Telescope-class \ac{GW} observatory~\cite{PhysRevD.81.123016}. Furthermore, in \ac{GW} detection efforts, especially those focused on \ac{BNS} systems, the component spins $\mathbf{S}_1$ and $\mathbf{S}_2$ are often assumed to be nonprecessing and aligned with the system's total angular momentum and condensed to a single scalar parameter $\chi$, or even neglected entirely, $\mathbf{S}_1 = \mathbf{S}_2 = 0$. In this work we will not consider spin precession.
